---
title: "p8105_hw3_yj2688"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)

library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Problem 1

```{r load dataset p8105}

data("instacart")


#Find number of aisles and aisle with most sales
instacart %>% 
  group_by(aisle_id) %>% 
  summarise(number_of_items = n()) %>%
  arrange(number_of_items) %>% 
  mutate(aisle_id = as.character(aisle_id)) %>%
  filter(number_of_items > 10000) %>%
  ggplot(aes(x = aisle_id, y = number_of_items)) + geom_col()+
  scale_x_discrete(guide = guide_axis(n.dodge=3)) +
  labs(title = "Number of Items Ordered in Aisles", x = "Aisle ID", y = "Number of Items")

```
There are 134 aisles. Aisle #24 has the most items ordered. 

```{r make a table for 3 aisles}

instacart %>% 
  filter(aisle == "baking ingredients" | aisle == "dog food care" | aisle == "packaged vegetables fruits") %>%
  select(product_id, product_name, aisle) %>% 
  group_by(aisle, product_name) %>%
  summarise(times_ordered = n()) %>%
  arrange(desc(times_ordered)) %>% 
  top_n(n=3)


```

Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r make table for mean hour of the day on condition}

instacart %>% 
  filter(product_name == "Pink Lady Apples" | product_name == "Coffee Ice Cream") %>%
  select(order_dow, order_hour_of_day, product_name) %>%
  group_by(product_name, order_dow) %>%
  summarise(mean_hour = mean(order_hour_of_day)) %>%
  pivot_wider(
    names_from  = "product_name",
    values_from = "mean_hour"
  ) %>%
  knitr::kable(digits = 2)

  

```

## Problem 2


```{r tidy accel dataset}
accel = read_csv(file = "./data/accel_data.csv", 
                 col_types = cols(.default = "c")) %>% 
  janitor::clean_names() %>%
  mutate(weekday_vs_weekend = if_else(day == 'Saturday'| day == 'Sunday', 'weekend', 'weekday'))

```

Describe the resulting data set: The resulting data set has 35 columns and 1444 rows. The weekday_vs_weekend column has 2 values, weekday or weekend, which represent the nature of the day when the activities were recorded. 

```{r aggregate across minutes to create a total activity variable for each day}
total = accel %>% 
  group_by(day_id) %>%
  mutate(total_activity = sum(activity_1:activity_1440)) %>%
  select(day_id, total_activity, weekday_vs_weekend)
```

Yes. The daily total activity count decreased over time, and the man is more active on weekends than on some weekdays. 

```{r make a single panel plot}
accel %>% 
  pivot_longer(activity_1:activity_1440, 
               names_to = 'minute',
               values_to = 'activity_count') %>%
  separate(col=minute, into=c('a', 'minute'), sep='_') %>%
  select(week, day_id, day, weekday_vs_weekend, minute, activity_count) %>%
  mutate(minute = as.numeric(minute), activity_count = as.numeric(activity_count), hour = minute/60) %>%
  mutate(hour = case_when(hour<=1 ~ 1, hour<=2 ~ 2, hour<=3 ~ 3, hour<=4 ~ 4,
                          hour<=5 ~ 5, hour<=6 ~ 6, hour<=7 ~ 7, hour<=8 ~ 8,
                          hour<=9 ~ 9, hour<=10 ~ 10, hour<=11 ~ 11, hour<=12 ~ 12,
                          hour<=13 ~ 13, hour<=14 ~ 14, hour<=15 ~ 15, hour<=16 ~ 16,
                          hour<=17 ~ 17, hour<=18 ~ 18, hour<=19 ~ 19, hour<=20 ~ 20,
                          hour<=21 ~ 21, hour<=22 ~ 22, hour<=23 ~ 23, hour<=24 ~ 24)) %>%
  select(-minute) %>%
  group_by(week, day_id, day, weekday_vs_weekend, hour) %>%
  summarize(activity_hour = sum(activity_count)) %>% 
  ggplot(aes(x = hour, y = activity_hour, color = day)) + geom_line() + 
  labs(
    title = "Activity Count Across 24 Hours Per Day",
    x = "Hour of the day",
    y = "Total Activity Per Hour") + 
  scale_x_continuous(
    breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20,
               21, 22, 23, 24), 
    labels = c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16",
               "17","18","19","20","21","22","23","24"))

  
  
  

  
```

##Problem 3

```{r load NYNOAA}

data("ny_noaa")
ny_no = ny_noaa %>% 
  separate(col=date, into=c('year', 'month', 'day'), sep='-') %>%
  mutate_at(c('tmin', 'tmax'), as.numeric) %>%
  replace(is.na(.), 0) %>% 
  group_by(id, year, month) %>% 
  summarise(mean_max = mean(tmax)) %>% 
  filter(month == "01" | month == "07")

ny_no
```